---
header-includes:
- \input{preamble.tex}
fontsize: 12pt
output: pdf_document
sansfont: roboto
font:     roboto
geometry: "left=1in,right=1in,top=0.35in,bottom=0.6in"
urlcolor: #169d62
---

\raggedright

```{r rmarkdown-setup, include=FALSE}
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")

dta <- data.frame(stringsAsFactors=FALSE,
                   Year = c("2012", "2012", "2012", "2012", "2012", "2016",
                            "2016", "2016", "2016", "2016", "Pooled", "Pooled",
                            "Pooled", "Pooled", "Pooled"),
               Estimate = c("Voter Registration", "Voter Registration",
                            "Voter Turnout", "Voter Turnout", "Voter Turnout",
                            "Voter Registration", "Voter Registration",
                            "Voter Turnout", "Voter Turnout", "Voter Turnout",
                            "Voter Registration", "Voter Registration", "Voter Turnout",
                            "Voter Turnout", "Voter Turnout"),
   `Universe(Denominator)` = c("Adult Population", "CVAP", "Adult Pop", "CVAP",
                            "Registered Voters", "Adult Population", "CVAP",
                            "Adult Pop", "CVAP", "Registered Voters",
                            "Adult Population", "CVAP", "Adult Pop", "CVAP",
                            "Registered Voters"),
            `Final Table` = c("2012_voterregistrationadultpop_table.csv",
                            "2012_voterregistrationcvap_table.csv",
                            "2012_votedadultpop_table.csv", "2012_votedcvap_table.csv",
                            "2012_votedregvoters_table.csv",
                            "2016_voterregistrationadultpop_table.csv",
                            "2016_voterregistrationcvap_table.csv", "2016_votedadultpop_table.csv",
                            "2016_votedcvap_table.csv", "2016_votedregvoters_table.csv",
                            "pooled_voterregistrationadultpop_table.csv",
                            "pooled_voterregistrationcvap_table.csv",
                            "pooled_votedadultpop_table.csv", "pooled_votedcvap_table.csv",
                            "pooled_votedregvoters_table.csv"),
          `Raw Crosstabs` = c("2012_voterregistrationadultpop.csv",
                            "2012_voterregistrationcvap.csv",
                            "2012_votedadultpop.csv", "2012_votedcvap.csv",
                            "2012_votedregvoters.csv", "2016_voterregistrationadultpop.csv",
                            "2016_voterregistrationcvap.csv", "2016_votedadultpop.csv",
                            "2016_votedcvap.csv", "2016_votedregvoters.csv",
                            "pooled_voterregistrationadultpop.csv",
                            "pooled_voterregistrationcvap.csv", "pooled_votedadultpop.csv",
                            "pooled_votedcvap.csv", "pooled_votedregvoters.csv")
)

```

\begin{figure}
  \hspace{-0.12in}
  \includegraphics[width=1.5in]{design/aapidata-logo-lighter.png}
  \label{fig:boat1}
\end{figure}

\urbntitle{CPS Voter Parity Analysis}
\urbnsubtitle{Data \& Methods Memo}

## Summary Information

I separated the estimates into separate tables by year and estimate. I also included estimates for 2012 and 2016, in case you want comparisons. Each table has the same set up with the following column names:

- `state` = State Name
-  `racial group` = Racial Group (Asian Alone, White non-Hispanic, Hispanic any race, Black)
-  `estimate` = the point estimate as a proportion
- ` low` = Low c.i.
- `high` = High c.i.


Here's a table with all the information:

```{r}
dta %>%
  kable( booktabs = T) %>% 
  kable_styling(latex_options="scale_down")
```
\contactinfo{}

\newpage
## Notes

All this data is located in this folder: 

- `AAPIData HQ/Projects/aapi_voter_sensitivity/`

### List of Files

- Raw CPS data that you were working with before: 
  
  `cps_voter_1216_pooled.dta`

- Dofile to get the file cleaned and ready to generated weighted estimates:

  `AAPIData HQ/Projects/aapi_voter_sensitivity/2018-08-30-pooledcps/coding.do`

- Finished estimates located here: 

  `aapi_voter_sensitivity/2018-08-30-pooledcps/finished_tables`