---
font: roboto
fontsize: 12pt
geometry: left=1in,right=1in,top=0.35in,bottom=0.6in
header-includes: \input{preamble.tex}
output:
  pdf_document: default
  word_document: default
sansfont: roboto
urlcolor: null
---

\raggedright

```{r rmarkdown-setup, include=FALSE}
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")

dta <- data.frame(stringsAsFactors=FALSE,
                  Table = c("full table (with text)", "full table (with text)", "full table (with text)",
                            "full table (with text)", "full table (with text)",
                            "slim table (with code ID)", "slim table (with code ID)", 
                            "slim table (with code ID)", "slim table (with code ID)", 
                            "slim table (with code ID)"),
               Estimate = c("question", "group_type", "group", "key", "value",
                            "questionID", "typeID", "groupID", "keyID", "value"),
   `Meaning` = c("survey question", "type of break-down", "groups within the break-down type",
                 "one key to the survey question", "percent of the group choosing the key",
                 "refer to questionID.xlsx", "refer to typeID.csv", "refer to groupID.csv",
                 "refer to keyID.csv", "percent of the group choosing the key"),
            `table file` = c("full_table.csv",
                             "full_table.csv",
                             "full_table.csv",
                             "full_table.csv",
                             "full_table.csv",
                             "slim_table.csv",
                             "slim_table.csv",
                             "slim_table.csv",
                             "slim_table.csv",
                             "slim_table.csv"),
          `Raw Crosstabs` = c("raw_survey_tables.xlsx", "raw_survey_tables.xlsx", "raw_survey_tables.xlsx", 
                              "raw_survey_tables.xlsx", "raw_survey_tables.xlsx", "raw_survey_tables.xlsx", 
                              "raw_survey_tables.xlsx", "raw_survey_tables.xlsx", "raw_survey_tables.xlsx", 
                              "raw_survey_tables.xlsx")
)

```

\begin{figure}
  \hspace{-0.12in}
  \includegraphics[width=1.5in]{design/aapidata-logo-lighter.png}
  \label{fig:boat1}
\end{figure}

\urbntitle{Asian American Voter Survey 2016 - Public Opinion Database}
\urbnsubtitle{Data \& Methods Memo}

## Summary Information

The data is extracted from cross table file `spring16aavs-crosstabs.xlsx` using tabula pdf extraction software. The extracted raw data raw_survey_tables.xlsx is divided into separate sheets: ethnic1, gender2, age3, nativity4 and geo based on the break-down groups in the cross table. There are geo5, geo6, geo7, geo8, geo9, geo10, geo11, geo12 and geo13 based on different geographic breakdowns. 

- The list of survey questions `questionID.xlsx` is extracted from the cross table file. `tableID` refers to the order of the tables from the original cross table file.
- `keyID.csv` refers to the survey question choices from all the tables. It is stored separately to reduce storage space.
- `groupID.csv` group breakdowns: Asian Indian, Chinese, Filipino,Male, Female, etc.
- `typeID.csv` refers to types of groups (ethnic, age, gender, nativity, geo1, geo2, ect)


```{r}
dta %>%
  kable( booktabs = T) %>% 
  kable_styling(latex_options="scale_down")
```
\contactinfo{}

\newpage
## Notes

All this data is located in this folder: 

- `Dropbox/AAPIData HQ/Projects/opinion database/AAVS-2016`

### List of Files

- Raw AAVS 2016 crosstab report: 
  `spring16aavs-crosstabs.pdf`

- Raw extracted crostab data: 
  `raw_survey_tables.xlsx`
  
- question ID lookup table: 
  `questionID.xlsx`

- key ID lookup table: 
  `keyID.csv`

- group ID lookup table: 
  `groupID.csv`

- Dofile to get the file cleaned and ready:
  `AAPIData HQ/Projects/opinion database/report_extract.R`
  
- type ID lookup table: 
  `typeID.csv`
  
- Full version table with text: 
  `full_table.csv`

- Slim version table with coded label: 
  `slim_table.csv`
  

